\documentclass[12pt,a4paper]{article}

% ── Packages ────────────────────────────────
\usepackage{graphicx}
\usepackage[margin=2.5cm, top=3cm, bottom=3cm]{geometry}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{caption}

% ── Colors ──────────────────────────────────
\definecolor{adpred}{HTML}{D0271D}
\definecolor{adpdark}{HTML}{1a1a2e}
\definecolor{adpgray}{HTML}{4B5563}
\definecolor{adplightgray}{HTML}{F8F9FA}
\definecolor{adpborder}{HTML}{DEE2E6}

% ── Page Layout ─────────────────────────────
\onehalfspacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{9pt}

% ── Header / Footer ─────────────────────────
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{{\color{adpred}\hrule width\headwidth height 0.4pt}}
\lhead{\small\color{adpgray}\textit{Nexus HCM — Internship Report}}
\rhead{\small\color{adpgray}\textit{GHARIANI Mohamed Amine}}
\cfoot{\small\color{adpgray}\thepage}

% ── Section Styling ─────────────────────────
\titleformat{\section}
  {\Large\bfseries\color{adpdark}}
  {\color{adpred}\thesection.}{0.5em}{}
  [\vspace{2pt}{\color{adpred}\titlerule[1.2pt]}\vspace{2pt}]

\titleformat{\subsection}
  {\normalsize\bfseries\color{adpdark}}
  {\color{adpgray}\thesubsection}{0.5em}{}

\titleformat{\subsubsection}
  {\normalsize\bfseries\color{adpgray}}
  {\thesubsubsection}{0.5em}{}

\titlespacing{\section}{0pt}{22pt}{8pt}
\titlespacing{\subsection}{0pt}{14pt}{4pt}
\titlespacing{\subsubsection}{0pt}{10pt}{4pt}

% ── Table Styling ────────────────────────────
\renewcommand{\arraystretch}{1.55}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

% ── List Styling ─────────────────────────────
\setlist[itemize]{leftmargin=1.5em, itemsep=3pt, topsep=4pt}
\setlist[enumerate]{leftmargin=1.5em, itemsep=3pt, topsep=4pt}

% ── Caption Styling ──────────────────────────
\captionsetup{
  font=small,
  labelfont={bf, color=adpgray},
  textfont=it,
  justification=centering
}

% ── Horizontal Rule Helper ───────────────────
\newcommand{\redrule}{\vspace{4pt}{\color{adpred}\hrule height 1pt}\vspace{4pt}}

% ─────────────────────────────────────────────
\begin{document}

% ════════════════════════════════════════════
% TITLE PAGE
% ════════════════════════════════════════════
\begin{titlepage}
\centering
\vspace*{1.5cm}

{\large\bfseries\color{adpdark}
  ESPRIT — École Supérieure Privée d'Ingénierie et de Technologies
}\\[0.3cm]
{\normalsize\color{adpgray} Engineering Degree in Computer Science}

\vspace{1.2cm}
{\color{adpborder}\rule{\linewidth}{0.5pt}}
\vspace{1.2cm}

{\fontsize{11}{13}\selectfont\color{adpgray}\textit{End-of-Studies Internship Report}}\\[0.6cm]
{\LARGE\bfseries\color{adpdark} Nexus HCM}\\[0.3cm]
{\Large\color{adpgray} Intelligent Human Capital Management System}

\vspace{0.8cm}
{\color{adpred}\rule{8cm}{1.2pt}}
\vspace{1.8cm}

\begin{minipage}{0.46\textwidth}
\begin{flushleft}
{\small\bfseries\color{adpgray} AUTHOR}\\[2pt]
{\normalsize\color{adpdark} GHARIANI Mohamed Amine}\\[0.7cm]
{\small\bfseries\color{adpgray} ACADEMIC SUPERVISOR}\\[2pt]
{\normalsize\color{adpdark} Amani Lamine}\\
{\small\color{adpgray}\ttfamily amani.lamine@esprit.tn}
\end{flushleft}
\end{minipage}
\hfill
\begin{minipage}{0.46\textwidth}
\begin{flushright}
{\small\bfseries\color{adpgray} HOST COMPANY}\\[2pt]
{\normalsize\color{adpdark} ADP ES Tunisie}\\
{\small\color{adpgray} Sana Business Center, Tunis}\\[0.7cm]
{\small\bfseries\color{adpgray} COMPANY SUPERVISOR}\\[2pt]
{\normalsize\color{adpdark} Ben Fraj Sayed}\\
{\small\color{adpgray}\ttfamily sayed.ben.fraj@adp.com}
\end{flushright}
\end{minipage}

\vfill
{\color{adpborder}\rule{\linewidth}{0.5pt}}\\[0.4cm]
{\small\color{adpgray} Academic Year 2025 — 2026}
\end{titlepage}

% ── Table of Contents ────────────────────────
\newpage
\tableofcontents
\newpage

% ════════════════════════════════════════════
% CHAPTER TITLE PAGE
% ════════════════════════════════════════════
\newpage
\thispagestyle{empty}
\vspace*{\fill}

\begin{center}
  {\color{adpred}\rule{4cm}{1.2pt}}\\[1.2cm]
  {\fontsize{13}{15}\selectfont\color{adpgray}\textit{Chapter 1}}\\[0.6cm]
  {\LARGE\bfseries\color{adpdark} Project Presentation and Framework}\\[1.2cm]
  {\color{adpred}\rule{4cm}{1.2pt}}
\end{center}

\vspace*{\fill}
\newpage

% ── 1. Introduction ──────────────────────────
\section{Introduction}

This chapter presents the general framework of the end-of-studies internship project carried out
at \textbf{ADP ES Tunisie}. It introduces the host organization, defines the objectives of the
requested work, analyzes the existing situation, and proposes a solution to address the identified
problems. Finally, it describes the project management methodology adopted throughout the
development process.

% ── 2. Presentation ──────────────────────────
\section{Presentation}

\subsection{Presentation of the Host Organization}

\textbf{ADP (Automatic Data Processing)} is one of the world's largest providers of Human Capital
Management (HCM) solutions, serving over 1 million clients across more than 140 countries.
Founded in 1949 in the United States, ADP offers a comprehensive suite of HR, payroll, talent
management, and workforce analytics services.

\textbf{ADP ES Tunisie} is the Tunisian subsidiary of ADP, located at the Sana Business Center,
Boulevard de l'Environnement, Tunis. The office operates as a technology and engineering center,
contributing to the development and maintenance of ADP's global HR software platforms.

\vspace{0.4cm}

\begin{center}
\begin{tabular}{C{4.5cm} C{7cm}}
\toprule
\textbf{Field} & \textbf{Information} \\
\midrule
Company Name    & ADP ES Tunisie \\
Sector          & Information Technology / HR Solutions \\
Headquarters    & Centre Urbain, Tunis 1003 \\
Email           & ADP.es@adp.com \\
Phone           & +216 71 110 606 \\
Website         & www.adp.com \\
\bottomrule
\end{tabular}
\captionof{table}{ADP ES Tunisie — Company Information}
\end{center}

\subsection{Objective of the Requested Work}

The objective of this internship is to design and develop a full-stack \textbf{Intelligent Human
Capital Management (HCM) Platform} — named \textit{Nexus HCM} — that centralizes and automates
the core HR operations within an enterprise environment.

The platform targets three distinct user roles:

\vspace{0.4cm}

\begin{center}
\begin{tabular}{C{3.5cm} L{9cm}}
\toprule
\textbf{Role} & \textbf{Responsibilities} \\
\midrule
HR Administrator &
  Manages the entire employee roster, provisions accounts, oversees all leave requests,
  attendance data, and system audit logs. \\
Manager &
  Supervises their direct team, approves or rejects leave requests, and monitors team
  attendance through a weekly calendar view. \\
Employee &
  Manages their personal profile, submits leave requests, and tracks attendance via a
  clock-in / clock-out mechanism. \\
\bottomrule
\end{tabular}
\captionof{table}{Platform User Roles and Responsibilities}
\end{center}

\subsection{Study of the Existing Situation}

\subsubsection{Analysis of Current HR Management Practices}

In many enterprises, HR management is still handled through a combination of disconnected tools:
spreadsheets for employee records, email chains for leave approvals, and manual timesheets for
attendance tracking. This fragmented approach leads to several operational challenges:

\begin{itemize}
  \item \textbf{Manual data entry} increases the risk of errors and inconsistencies in employee records.
  \item \textbf{Lack of a unified platform} forces HR teams to switch between multiple tools, reducing productivity.
  \item \textbf{No real-time visibility} over workforce availability, pending leave requests, or attendance patterns.
  \item \textbf{Absence of an audit trail} makes it difficult to track who performed which HR action and when.
  \item \textbf{Poor onboarding experience} for new employees, who often receive credentials through insecure channels.
\end{itemize}

\subsubsection{Critique of the Existing Situation}

The analysis of the current state reveals the following critical weaknesses:

\vspace{0.4cm}

\begin{center}
\begin{tabular}{C{5.5cm} C{7.5cm}}
\toprule
\textbf{Identified Problem} & \textbf{Impact on the Organization} \\
\midrule
No centralized employee database &
  Data scattered across files and emails, leading to inconsistencies \\
Manual leave approval process &
  Slow response times, no traceability, risk of lost requests \\
No attendance tracking system &
  Impossible to monitor punctuality, absences, or overtime \\
No role-based access control &
  Sensitive HR data accessible to unauthorized personnel \\
No onboarding automation &
  New employees receive credentials through insecure channels \\
No audit logging &
  No accountability or traceability for HR actions \\
\bottomrule
\end{tabular}
\captionof{table}{Critique of the Existing HR Management Situation}
\end{center}

% ── 3. Proposed Solution ─────────────────────
\section{Proposed Solution}

\subsection{Objectives of the Proposed Solution}

The proposed solution, \textbf{Nexus HCM}, is a centralized, intelligent HR management platform
that directly addresses all identified weaknesses. Its core objectives are:

\begin{enumerate}
  \item Provide a \textbf{single unified platform} for all HR operations.
  \item Automate the \textbf{employee onboarding} process with secure token-based account activation.
  \item Implement \textbf{role-based access control} to protect sensitive HR data.
  \item Enable \textbf{real-time leave management} with a structured approval workflow.
  \item Track \textbf{employee attendance} through a digital clock-in / clock-out system.
  \item Maintain a complete \textbf{audit trail} of all HR operations.
  \item Integrate an \textbf{AI-powered report generation} feature using an external AI API.
\end{enumerate}

\subsubsection{Objective Comparison: Existing vs.\ Proposed Solution}

\vspace{0.4cm}

\begin{center}
\begin{tabular}{C{4.2cm} C{4.2cm} C{4.2cm}}
\toprule
\textbf{Feature} & \textbf{Existing Approach} & \textbf{Nexus HCM} \\
\midrule
Employee Management  & Manual / Spreadsheets    & Centralized digital roster \\
Leave Approval       & Email-based              & Automated approval workflow \\
Attendance Tracking  & Paper timesheets         & Digital clock-in / clock-out \\
Role-Based Access    & None                     & HR Admin / Manager / Employee \\
Onboarding           & Manual                   & Token-based email activation \\
Audit Trail          & None                     & Full operation history log \\
Reporting            & Manual                   & AI-generated smart reports \\
\bottomrule
\end{tabular}
\captionof{table}{Comparison: Existing Situation vs.\ Nexus HCM}
\end{center}

% ── 4. Project Management ────────────────────
\section{Project Management}

\subsection{Adopted Methodology}

\subsubsection{Choice of Methodology}

For this project, the \textbf{V-Model} (Verification and Validation Model) was selected as the
development methodology. This choice is justified by the structured and well-defined nature of
the project requirements, established at the beginning of the internship in collaboration with
the company supervisor.

The V-Model is particularly suited for this project because:

\begin{itemize}
  \item The requirements are clearly defined and unlikely to change significantly.
  \item Each development phase has a corresponding testing phase, ensuring quality at every level.
  \item It provides a clear and traceable path from requirements to final delivery.
\end{itemize}

\subsubsection{Presentation of the V-Model}

The V-Model is a sequential software development process in which each development phase is
directly associated with a corresponding testing phase. The left side of the ``V'' represents
the decomposition of requirements and system design, while the right side represents the
integration and verification of each component.

\vspace{0.4cm}

\begin{center}
\begin{tabular}{C{5cm} C{2cm} C{5cm}}
\toprule
\textbf{Development Phase} & & \textbf{Verification Phase} \\
\midrule
Requirements Analysis  & $\longleftrightarrow$ & Acceptance Testing \\
System Design          & $\longleftrightarrow$ & System Testing \\
Architecture Design    & $\longleftrightarrow$ & Integration Testing \\
Module Design          & $\longleftrightarrow$ & Unit Testing \\
\midrule
\multicolumn{3}{c}{\textit{Implementation — Center of the V}} \\
\bottomrule
\end{tabular}
\captionof{table}{V-Model Development and Verification Phases}
\end{center}

\subsubsection{Roles in the V-Model}

\vspace{0.4cm}

\begin{center}
\begin{tabular}{C{4cm} C{8.5cm}}
\toprule
\textbf{Role} & \textbf{Responsibility} \\
\midrule
Developer       & Implements features according to design specifications \\
Tester          & Validates each module against its corresponding requirements \\
Project Manager & Ensures timeline adherence and milestone delivery \\
HR Stakeholder  & Validates functional requirements and acceptance criteria \\
\bottomrule
\end{tabular}
\captionof{table}{Team Roles in the V-Model}
\end{center}

% ── 5. Conclusion ────────────────────────────
\section{Conclusion}

This chapter provided a comprehensive overview of the project framework. It introduced
\textbf{ADP ES Tunisie} as the host organization, analyzed the limitations of current HR
management practices, and presented \textbf{Nexus HCM} as a structured solution to these
challenges. The adoption of the V-Model methodology ensures a disciplined and quality-driven
development process throughout the six-month internship period.

The following chapters will detail the technical design, system architecture, implementation,
and testing of each module of the platform.

\end{document}
